---
title: "logistic regression"
author: "Drs Kand J"
date: '2022-06-11'
output: html_document
---

```{r}
library(tidyverse)
library(tigerstats)
library(Sleuth2)

donnerData = case2001
```




```{r}

logRegModel = glm(Status~Age + Sex, family = binomial, data=donnerData)
Age = donnerData$Age
sexCoded = ifelse(donnerData$Sex=='Male',1,0)

logRegModel$coefficients
```
## (Intercept)         Age   SexFemale 
##  1.63312031 -0.07820407  1.59729350

```{r}

eta = logRegModel$coefficients[1]+ logRegModel$coefficients[2]*Age + logRegModel$coefficients[2]*sexCoded

summary(logRegModel)
```
## 
## Call:
## glm(formula = Status ~ Age + Sex, family = binomial, data = donnerData)
## 
## Deviance Residuals: 
##     Min       1Q   Median       3Q      Max  
## -1.7445  -1.0441  -0.3029   0.8877   2.0472  
## 
## Coefficients:
##             Estimate Std. Error z value Pr(>|z|)  
## (Intercept)  1.63312    1.11018   1.471   0.1413  
## Age         -0.07820    0.03728  -2.097   0.0359 *
## SexFemale    1.59729    0.75547   2.114   0.0345 *
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## (Dispersion parameter for binomial family taken to be 1)
## 
##     Null deviance: 61.827  on 44  degrees of freedom
## Residual deviance: 51.256  on 42  degrees of freedom
## AIC: 57.256
## 
## Number of Fisher Scoring iterations: 4

```{r}

probIndivid = function(age, sex){
  pSurviv = logRegModel$coefficients[1]+ logRegModel$coefficients[2]*age + logRegModel$coefficients[2]*sex
  return(exp(pSurviv)/(1+exp(pSurviv)))
}

prob = function(eta){
  prob = exp(eta)/(1+exp(eta)) 
}
```

## prob plot
```{r}
etaWomen = logRegModel$coefficients[1]+ logRegModel$coefficients[2]*Age + logRegModel$coefficients[2]*0
etaMen = logRegModel$coefficients[1]+ logRegModel$coefficients[2]*Age + logRegModel$coefficients[2]*1
plot(eta, prob(etaWomen),type='p')
points(eta, prob(etaMen), type='p', col='red')
```